---
title: "Insight Data Analysis"
format: html
editor: visual
---

## **Insight Data Analysis**

**Understand the Dataset Structure**:

```{r}
library(readxl)
airbnb_data <- read_excel("airbnb_data.xlsx")
library (ggplot2)
str(airbnb_data)
```

**Summary Statistics**:

```{r}
summary(airbnb_data)
```

**Visualizations**:

Use **`ggplot2`** to visualize relationships and distributions, for example:

```{r}
ggplot(airbnb_data, aes(x=price)) + geom_histogram(bins=50)
ggplot(airbnb_data, aes(x=neighbourhood_group, y=price)) + geom_boxplot()

```

**Check for Missing Values**:

```{r}
sapply(airbnb_data, function(x) sum(is.na(x)))

```

**Data Cleaning and Preprocessing**

-   **Handle Missing Values**: Impute or remove missing values depending on their impact.

-   **Feature Selection**: Choose relevant features for your model. For example, predicting **`price`** based on **`room_type`**, **`number_of_reviews`**, etc.

-   **Encoding Categorical Variables**: Use one-hot encoding for categorical variables.

-   **Data Transformation**: Normalize or scale numerical features if necessary.

    **Building a Linear Regression Model**

    **Simple Linear Regression**:

    ```{r}
    model_simple <- lm(price ~ number_of_reviews, data=airbnb_data)
    summary(model_simple)
    ```

**Multiple Linear Regression**:

```{r}
model_multiple <- lm(price ~ neighbourhood_group + room_type + number_of_reviews, data=airbnb_data)
summary(model_multiple)

```

**Model Diagnostics**

-   Check assumptions of linear regression such as linearity, homoscedasticity, and normality of residuals.

**Model Validation**

-   Use cross-validation to assess model performance.

**Model Improvement**

-   Explore different combinations of features.

-   Consider transforming features or using polynomial terms for non-linear relationships.

**Conclusion**

This process offers a systematic approach to building a linear regression model using the NYC Airbnb dataset. It's essential to understand each step thoroughly for robust model development and accurate insights.
